\mireval{}: A Transparent Implementation of Common MIR Metrics

### 2014-07-02 paper/paper.tex
Changing authors and title

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
%\usepackage{authblk}
\usepackage{booktabs}

@@

\title{\mireval{}}

\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}

%\author[1]{Colin Raffel}
%\author[1]{Brian McFee}
%\author[2]{Eric J. Humphrey}
%\author[2]{Justin Salamon}
%\author[2]{Oriol Nieto}
%\author[1]{Dawen Liang}
%\author[1]{Daniel P. W. Ellis}
%\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
%\affil[2]{Music and Audio Research Lab\\New York University, New York}

>>>>

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
\usepackage{authblk}
\usepackage{booktabs}

@@

\title{\mireval{}: A Transparent Implementation of Common MIR Metrics}

%\threeauthors
%  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
%  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
%  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}

\author[1]{Colin Raffel}
\author[1]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}
